---
title: "gala"
author: "zhengzihaosqs"
date: "2019-10-20"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

At first, we input data from local csv file for further analysis.

```{r}
library(readr)
mydata <- read.csv("MyData.csv")
mydata
```

This dataset describe some information about species diversity on the Galapagos Islands, the first column is the names of the island, and for other columns their meanings are: 

Species:--the number of plant species found on the island

Endemics:--the number of endemic species

Area:--the area of the island (km$^2$)

Elevation:--the highest elevation of the island (m)

Nearest:--the distance from the nearest island (km)

Scruz:--the distance from Santa Cruz island (km)

Adjacent:--the area of the adjacent island (square km)

We show descriptive statistics for Species and Area:

```{r}
summary(mydata$Species)
sd(mydata$Species)
summary(mydata$Endemics)
sd(mydata$Endemics)
```

Information about mean, median, the minimum and maximum value, quantile points and standard deviation for two columns are shown above.

Now we are going to add plots to reveal more feature of these two columns.

```{r distribution}
par(mfrow=c(1,2))
hist(mydata$Species,main="Histogram of Species",xlab="Species")
hist(mydata$Endemics,main="Histogram of Endemics",xlab="Endemics")
```

We plot two histograms to show the distributions of two columns, but we can not see much information from histograms. So we decide plot a scatterplot to show the relationship between two columns.

```{r scatter plot}
par(mfrow=c(1,1))
plot(mydata$Species,mydata$Endemics,main="Scatterplot of Species and Endemics",xlab="Species",ylab="Endemics")
```

We can see a positive correlation between them.

Now we run a simple linear regression to estimate the relationship between Endemics and Species

```{r}
lmd<-lm(Endemics~Species,mydata)
slmd<-summary(lmd)
slmd
```

From the summary information of the regression result, we see that the p-value for intercept and species is `r slmd$coef[1,4]` and `r slmd$coef[2,4]`, which means the covariate and intercept terms are significant. 

The estimated value of intercept is `r slmd$coef[1,1]` and the estimated value of Species is `r slmd$coef[2,1]`. We add the fitted line to the scatterplot:

```{r}
plot(mydata$Species,mydata$Endemics,main="Scatterplot of Species and Endemics")
abline(lmd)
```

We can see that the linear model fits the data well.
